%Ever growing field of HPC requires parallel benchmarks to facilitate research in architecture, programming languages, and operating systems. Rodinia currently presents OpenMP and CUDA implementations of a set of applications to use as benchmarks in the architecture, compiler, and programming-language research. It provides codes, which are reference implementations for research on parallelizing compilers as well as design patterns. For users to develop their own parallel codes, the benchmark is basically intended to evaluate the performance of heterogeneous computing. It incorporates applications and distinguishes kernels targeting the multicore architectures. To reflect major computational kernels in real-world scientific and engineering applications, this work focuses on five representative benchmarks, i.e., LUD, CFD, NW, BFS and HotSpot. Table \ref{tab:benchmarks} provides a summary of Berkeley dwarves \cite{asanovic2006landscape}, domains and problem size for the benchmarks. 

Ever growing field of HPC requires parallel benchmarks to facilitate research in architecture, programming languages, and operating systems. Rodinia currently presents OpenMP and CUDA implementations of a set of applications kernels targeting the multicore architectures. To reflect major computational kernels in real-world scientific and engineering applications, this work focuses on five representative benchmarks, i.e., LUD, CFD, NW, BFS and HotSpot. Table \ref{tab:benchmarks} provides a summary of domains and problem size for the benchmarks. 


LU Decomposition (LUD) is an algorithm to calculate the solutions of a set of linear equations. The LUD kernel decomposes a matrix as the product of a lower triangular matrix and an upper triangular matrix. This application has many row-wise and column-wise interdependencies and requires significant optimization to achieve good parallel performance.



Computational Fluid Dynamics (CFD) is an unstruct-ured-grid, finite-volume solver for the three-dimensional Euler equations for compressible flow. Effective GPU memory bandwidth is improved by reducing total global memory accesses and overlapping redundant computation, as well as by using an appropriate numbering scheme and data layout. The CFD solver is released with two versions: one with pre-computed fluxes, and the other with redundant flux computations.

%\vspace{-2mm}

    % Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
    \caption{RODINIA BENCHMARK SUITE}
  \begin{adjustbox}{width=0.5\textwidth}
    \begin{tabular}{cccc}
    \toprule
    Applications & Dwarves & Domains & Problem Size  \\
    \midrule
    LUD & Dense Linear Algebra & Linear Algebra & 12000 \\
    CFD & Unstructured Grid & Fluid Dynamics & 193000 \\
    NW & Dynamic Programming & Bioinformatics & 32000 \\
    BFS & Graph Traversal & Graph Algorithms & 64Million \\
    HotSpot & Structured Grid & Physics Simulation & 1024 \\
    \bottomrule
    \end{tabular}%
    \label{tab:benchmarks}
  \end{adjustbox}

\end{table}% 

%\vspace{-1mm}

  Needleman-Wunsch (NW) is a dynamic programming algorithm for sequence alignments, which builds up the best alignment by using optimal alignments of smaller subsequences. It consists of three steps: initialization of the score matrix, calculation of scores, and deducing the alignment from the score matrix.

  Breath-First Search (BFS) is the Breadth-First Search that is an algorithm for traversing or searching tree or graph data structures and explores the neighbor nodes first before moving to the next level neighbored.

  HotSpot is a widely used tool to estimate processor temperature based on an architectural floor plan and simulated power measurements. The thermal simulation iteratively solves a series of differential equations for block. Each output cell in the computational grid represents the average temperature value of corresponding area of the chip.